Modelling potential environmental impacts of science activity in Antarctica

### 2025-09-24 talk/index.qmd
some more minor edits to slides

##
![](fig-study-area-1.png)

@@

## Hiking functions
![](fig-hiking-functions-1.png)

## Smoothing GPS data
![](fig-gps-data-1.png)

## Curve fitting to cleaned data
![](fig-comparison-of-hiking-functions-1.png)

## Terrain-dependent _vs_ combined
![](fig-models-by-cover-compared-1.png)

@@

##
![](fig-hiking-network-example-1.png)

@@

![](fig-betweenness-map-1.png)

@@

![](fig-radius-limited-betweenness-1.png)

@@

![](fig-betweenness-limited-sites-1.png)

@@

![](fig-approx-minimum-arborescence-1.png)

@@

# {background-image="background-image.png"}
[Questions?]{style="font-size:200px;color:black;opacity:25%;text-align:center;"}

>>>>

##
![](fig-study-area-1.png){fig-align="center"}

@@

## Hiking functions
![](fig-hiking-functions-1.png){fig-align="center"}

## Smoothing GPS data
![](fig-gps-data-1.png){fig-align="center"}

## Curve fitting to cleaned data
![](fig-comparison-of-hiking-functions-1.png){fig-align="center"}

## Terrain-dependent _vs_ combined
![](fig-models-by-cover-compared-1.png){fig-align="center"}

@@

##
![](fig-hiking-network-example-1.png){fig-align="center"}

@@

![](fig-betweenness-map-1.png){fig-align="center"}

@@

![](fig-radius-limited-betweenness-1.png){fig-align="center"}

@@

![](fig-betweenness-limited-sites-1.png){fig-align="center"}

@@

![](fig-approx-minimum-arborescence-1.png){fig-align="center"}

@@

# {background-image="background-image.png"}

### Questions? {style="font-size:220px;color:black;opacity:25%;text-align:center;font-weight:700;"}

::: {style="background-color:rgba(102,0,0,0.1);"}
<h2 style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);">For more</h2>
### On this project [dosull.github.io/antarctica](https://dosull.github.io/antarctica) {style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);"}
### About ![](logo.png){style="vertical-align:middle;width:60px;text-align:center;"} Geospatial Stuff [dosull.github.io](https://dosull.github.io) {style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);"}
:::
